Introductory statistics with `intRo`

### 2016-02-19 jcgs-paper-2016/paper.Rmd
Sections

Upon the release of RStudio's Shiny [@shiny] it became easier for an R-based analysis to be converted to an interactive web application. This in turn led us to create an introductory statistics application which we call `intRo`, available at http://www.intro-stats.com. `intRo` offers a number of key advantages over traditional statistics software, including ease of use and an aim to foster student interest in coding. Additionally, `intRo` stands apart from new tools in that it is a supplement to an existing class, fully usable by a beginning statistics student. These advantages will be discussed at length in this text.

>>>>

Upon the release of RStudio's Shiny [@shiny] it became easier for an R-based analysis to be converted to an interactive web application. This in turn led us to create an introductory statistics application which we call `intRo`, available at http://www.intro-stats.com. `intRo` offers a number of key advantages over traditional statistics software, including ease of use and an aim to foster student interest in coding. Additionally, `intRo` stands apart from new tools in that it is a supplement to an existing class, fully usable by a beginning statistics student. These advantages will be discussed at length in this text. The paper is structured as follows: Section 2 introduces the application, its features and its usability. Section 3 describes the process of creating a classroom instance of `intRo` tailored to the individual instructor. Section 4 provides technical details on the implementation of `intRo`. Finally, Section 5 discusses some future possibilities and limitations of the software.
